HUME: Human UCCA-Based Evaluation of Machine Translation

### 2016-03-17 paper/main.tex
www

In order to validate the HUME metric, we ran an annotation experiment with one source language (English), and four 
target languages (Czech, German, Polish and Romanian), using text from the public health domain.
The domain is particularly suitable for experimenting on MT evaluation, as being able to determine
whether the translation accurately conveys the same information as the source is here paramount.

@@

%\subsection{Data}\label{sec:data}

%\subsection{Efficiency of Annotation}\label{sec:efficiency}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Human Semantic Evaluation}

@@

UCCA provides universal semantic structures which 
%has 
have
a minimal set of labels. It provides a complete semantic tree which does not rely on syntactic heads and the semantic structure is grounded directly to the words in the sentence. 
 Even though the set of UCCA labels are fairly restricted,  nevertheless they allow us to determine the most important components of the graph (for example it defines centres and linkers which would be likely to carry more weight than elaborators), and we can use this to better calculate the score. 
We think that UCCA is the
most promising representation for evaluating translation.

@@

\section*{Acknowledgments}

Do not number the acknowledgment section.
This section should not be presented for the submission version.

>>>>

In order to validate the HUME metric, we ran an annotation experiment with one source language (English),
and four target languages (Czech, German, Polish and Romanian), using text from the public health domain.
The domain is particularly suitable for experimenting on MT evaluation, as semantically
accurate translation is paramount here, underscoring the importance of accurate
semantic evaluation measures.

@@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\com{
\section{Human Semantic Evaluation}

@@

UCCA provides universal semantic structures which 
%has 
have
a minimal set of labels. It provides a complete semantic tree which does not rely on syntactic heads and the semantic structure is grounded directly to the words in the sentence. 
 Even though the set of UCCA labels are fairly restricted,  nevertheless they allow us to determine the most important components of the graph (for example it defines centres and linkers which would be likely to carry more weight than elaborators), and we can use this to better calculate the score. 
We think that UCCA is the
most promising representation for evaluating translation. 
}

@@

%\section*{Acknowledgments}

%Do not number the acknowledgment section.
%This section should not be presented for the submission version.
